---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "README_figs/README-")
```
# PWN workflow for the detection of declining trees using MaxEnt

Authors: 
    + Pieter Beck
    + Laura Martinez

Date: March, 2018

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active) 

# To do

* Finish the workflow by adding the potsprocessing function

# CanHeMonR.MaxEnt

The goal of CanHeMonR.MaxEnt is to create a workflow to detect declining trees in aerial images through MaxEnt library

## Installation

You can install CanHeMonR.MaxEnt from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MartinezLaura/CanHeMonR-Maxent")
```

## Example
check the Markdown document called main-Markdown.Rmd to see an example and description of the functions 
