---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "README_figs/README-")
```
---
title: "PWN workflow for the detection of declining trees using MaxEnt"
author: "Pieter Beck", "Laura Martinez"
date: "March, 2018"
---

# To do

* Finish the workflow by adding the potsprocessing function

# CanHeMonR.MaxEnt

The goal of CanHeMonR.MaxEnt is to create a workflow to detect declining trees in aerial images through MaxEnt library

#Algorithm flowchart
```{r, echo=FALSE}
DiagrammeR::DiagrammeR("
graph TB
    A>Point shapefile with precences] --> D[Sample presences and backgroud points]
    B>Raster files and textures to run] --> D
    C>Biased tifs] --> D
    D --> E>Serialize object with the points]
    E --> F[Calibration and creation of MaxEnt model]
    F --> G>serialize object with the model]
    G --> H[Run model over the tiles]
    B --> H
")
```

## Installation

You can install CanHeMonR.MaxEnt from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("MartinezLaura/CanHeMonR-Maxent")
```

## Example
chack the Markdown document called main-Markdown.Rmd to see an example and description of the functions 
